---
title: "R Packages"
description: "These are the R packages that I've developed or currently developing. You can find the source code and installation instructions on my github page."
toc: true
toc-location: left
---

```{r}
#| echo: false
#| message: false
library(ggplot2)
library(owidR)
library(statxplore)
library(ukmap)

my_theme <- function() {
    theme_owid(import_fonts = FALSE) + 
    theme(axis.title = element_blank(), text = element_text(size = 20), plot.title = element_text(size = 34), 
          plot.background = element_rect(fill = "#F0F6FF", colour = "#718199"), legend.position = "none")
} 

theme_set(my_theme())
```


## [owidR](https://github.com/piersyork/owidR)
This package imports data from [Our World in Data](https://ourworldindata.org) into the R environment. Our World in Data collect and publish hundreds of country level datasets on economic and social issues. owidR makes it easy to search through these datasets, load them into R and quickly visualise the data. You can download owidR from CRAN using `install_packages("owidR")`. Here is an example using data on democracy:

```{r}
# search for dataset titles that begin with 'liberal democracy'
owid_search("^liberal democracy")

# let's use the liberal democracy data from varieties of democracy
lib_democ <- owid("liberal-democracy")

lib_democ

```


## [statxplore](https://github.com/piersyork/statxplore)
This packages imports data from the Department for Work and Pensions' [statXplore](https://stat-xplore.dwp.gov.uk/) repository of published statistics on pensions and benefits. This package is currently in the early stages of development and not yet published on CRAN. Here is an example:

```{r}
#| eval: false
API_KEY <- "YOUR_API_KEY"

pip_regs_age <- start_query("Personal Independence Payment", "PIP Registrations", API_KEY) |>
  add_measure("PIP Registrations") |>
  add_fields(c("Month", "Age (bands and single year)")) |>
  fetch()

pip_regs_age
```

```{r}
#| echo: false
#| warning: false
API_KEY <- readLines(".statX_key.txt")

pip_regs_age <- start_query("Personal Independence Payment", "PIP Registrations", API_KEY) |>
  add_measure("PIP Registrations") |>
  add_fields(c("Month", "Age (bands and single year)")) |>
  fetch()

pip_regs_age
```



## [ukmap](https://github.com/piersyork/ukmap)
This package is a wrapper around the Office for National Statistics' [geospatial API](https://statistics.data.gov.uk/home). It is currently experimental but allows for the easy importing of geospatial data into R of class `sf`. At the moment the API only allows fetching of the most recent UK geography data. 


```{r}
#| results: 'hide'
#| warning: false
# get map data for london boroughs
london <- uk_codes("E09") |> 
  uk_map()

# use the tmap package to easily see what the map data looks like
tmap::qtm(london)
```

